\begin{thebibliography}{99}
    \bibitem{先天的能力} \
    Zador, Anthony M. \
    "A critique of pure learning and what artificial neural networks can learn from animal brains." \
    Nature communications 10.1 (2019): 3770.
    
    \bibitem{WANN} \
    Gaier, Adam, and David Ha. \
    "Weight agnostic neural networks." \
    Advances in neural information processing systems 32 (2019).

    \bibitem{NEAT} \
    Stanley, Kenneth O., and Risto Miikkulainen. \
    "Evolving neural networks through augmenting topologies." \
    Evolutionary computation 10.2 (2002): 99-127.

    \bibitem{遺伝的アルゴリズム} \
    坂和正敏, 田中雅博. \
    "遺伝的アルゴリズム" 朝倉書店 (2002).
    
    \bibitem{NE} \
    Braun, Heinrich, and Joachim Weisbrod. \
    "Evolving neural feedforward networks." \
    Artificial Neural Nets and Genetic Algorithms: Proceedings of the International Conference in Innsbruck, Austria, 1993. Vienna: Springer Vienna, 1993.

    \bibitem{深層学習} \
    伊庭斉志. \
    "進化計算と深層学習 -創発する知能-" オーム社 (2015). 

    \bibitem{活性化関数} \
    Dubey, Shiv Ram, Satish Kumar Singh, and Bidyut Baran Chaudhuri. \
    "Activation functions in deep learning: A comprehensive survey and benchmark." \
    Neurocomputing (2022).

    \bibitem{距離関数} \
    青嶋誠, 矢田和善. \
    "高次元の統計学" 共立出版 (2019).

    \bibitem{ノード入力} \
    Glorot, Xavier, and Yoshua Bengio. \
    "Understanding the difficulty of training deep feedforward neural networks." \
    Proceedings of the thirteenth international conference on artificial intelligence and statistics. JMLR Workshop and Conference Proceedings, 2010.

    \bibitem{シナプス学習} \
    Black, James E., et al. \
    "Learning causes synaptogenesis, whereas motor activity causes angiogenesis, in cerebellar cortex of adult rats." \
    Proceedings of the National Academy of Sciences 87.14 (1990): 5568-5572.

    \bibitem{OpenAI} \
    Brockman, Greg, et al. \
    "Openai gym." \
    arXiv preprint arXiv:1606.01540 (2016).
\end{thebibliography}